Equalizer\\Programming and User Guide

### 2012-01-27 Developer/ProgrammingGuide/paper.tex
Finish PG review for Eq 1.2

\date{
  \vspace{14cm}
\begin{textblock}{}(0,4.5)
  \hspace{-1cm}\includegraphics[width=22cm]{images/teaser.pdf}
\end{textblock} {\Large The official reference for developing and
  deploying parallel, scalable OpenGL\texttrademark\ applications using
  the Equalizer parallel rendering framework}\\\vspace{1cm}
Version 1.8.4 for Equalizer 1.1.5+git \\[\medskipamount]
%  \today
}

@@

\clearpage
\pagenumbering{roman}
\pagestyle{headings}
\tableofcontents
%\clearpage
\listoffigures \vfill
\section*{Revision History}
{\center\begin{tabularx}{\textwidth}{|l|l|X|}
    \hline
    \bf Rev & \bf Date     & \bf Changes \\
    \hline
    1.0     & Oct 28, 2007 & Initial Version for Equalizer 0.4\\
    1.2     & Apr 15, 2008 & Revision for Equalizer 0.5\\
    1.4     & Nov 25, 2008 & Revision for Equalizer 0.6\\
    1.6     & Aug 07, 2009 & Revision for Equalizer 0.9\\
    1.8     & Mar 21, 2011 & Revision for Equalizer 1.0\\
    1.8.1   & Mar 25, 2011 & Minor Revision\\
    1.8.2   & Apr 04, 2011 & Added \sref{sFocusDistance}\\
    1.8.3   & Aug 10, 2011 & Rewrote \sref{sHello}\\
    1.8.4   & Nov 18, 2011 & Added \sref{sAutoConfig}\\
    \hline
  \end{tabularx}}
\clearpage

@@

\begin{tabularx}{\textwidth}{|l|X|}
  \hline
  \textbf{Name} & EQ\_CONFIG\_FATTR\_EYE\_BASE\\
  \textbf{Value} & float\\
  \textbf{Default} & 0.05\\
  \textbf{Details} & The default distance in meters between the left and
  the right eye, i.e., the eye separation. The eye base influences the
  frustum during stereo rendering. See \sref{sTracking} for details.\\
  \textbf{See also} & EQ\_WINDOW\_IATTR\_HINT\_STEREO
  EQ\_COMPOUND\_IATTR\_STEREO\_MODE\\
  \hline
\end{tabularx}\\\vfill

@@

\begin{tabularx}{\textwidth}{|l|X|}
  \hline
  \textbf{Name} & EQ\_COMPOUND\_IATTR\_STEREO\_ANAGLYPH\_LEFT\_MASK\\
  \textbf{Value} & [ RED GREEN BLUE ]\\
  \textbf{Default} & [ RED ] \\
  \textbf{Details} & Select the color mask for the left eye pass during
  anaglyphic stereo rendering.\\
  \hline
\end{tabularx}\\

@@

{\footnotesize\lstinputlisting[firstline=87, lastline=96]
  {../../../equalizergraphics.com/documents/design/fileFormat.shtml}}

@@

{\footnotesize\lstinputlisting[firstline=98, lastline=105]
  {../../../equalizergraphics.com/documents/design/fileFormat.shtml}}

@@

A node represents a machine in the cluster, and is one process. It has a
name, a number of connection descriptions and at least one pipe. The
name of the node can be used for debugging, it has no influence on the
execution of Equalizer. For a description of node and connection
attributes please refer to \sref{sGlobal}.

{\footnotesize\lstinputlisting[firstline=107, lastline=125]
  {../../../equalizergraphics.com/documents/design/fileFormat.shtml}}

@@

For the WGL window system, the device selects the \textit{n}th GPU in
the system. The GPU can be offline, in this case only PBuffer windows
can be used. To restrict the OpenGL output to the GPU, the
\textsf{WGL\_NV\_gpu\_affinity} extension is used. If the extension is
not present, the window is opened on the \textit{n}th monitor, but
OpenGL commands are sent to a different or all GPU's.

@@

{\footnotesize\lstinputlisting[firstline=125, lastline=136]
  {../../../equalizergraphics.com/documents/design/fileFormat.shtml}}

@@

{\footnotesize\lstinputlisting[firstline=136, lastline=158]
  {../../../equalizergraphics.com/documents/design/fileFormat.shtml}}

@@

@@

{\footnotesize\lstinputlisting[firstline=158, lastline=167]
  {../../../equalizergraphics.com/documents/design/fileFormat.shtml}}

@@

An observer represents a tracked entity, i.e, one user. It has a name
and an eye separation. The name of an observer can be used for
debugging, it has no influence on the execution of Equalizer. It can be
used to reference the observer in views, in which case the name should
be unique. Not all views have to be tracked by an observer.

{\footnotesize\lstinputlisting[firstline=172, lastline=176]
  {../../../equalizergraphics.com/documents/design/fileFormat.shtml}}

@@

{\footnotesize\lstinputlisting[firstline=178, lastline=181]
  {../../../equalizergraphics.com/documents/design/fileFormat.shtml}}

@@

A view has a stereo mode, which defines if the corresponding destination channel
update the cyclop or left and right eye.

@@

{\footnotesize\lstinputlisting[firstline=181, lastline=202]
  {../../../equalizergraphics.com/documents/design/fileFormat.shtml}}

@@

Each canvas is made of one or more segments. Segments can be planar or
non-planar to each other, and can overlap or have gaps between each
other. A canvas can define a frustum, which will create default planar
sub-frusta for its segments.

The layouts referenced by the canvas can be applied to it by the
application at runtime. One layout can be referenced by multiple
canvases. The first layout is the layout active by default.

{\footnotesize\lstinputlisting[firstline=205, lastline=225]
  {../../../equalizergraphics.com/documents/design/fileFormat.shtml}}

@@

A segment represents a single display, i.e., a projector or monitor. It
references a channel, has a name, viewport and frustum. The name of a
segment can be used for debugging, it has no influence on the execution
of Equalizer. It can be used to reference the segment, in which case the
name should be unique.

The channel referenced by the segment defines the output channel. The
viewport of the section defines the 2D area covered by the channel on
the canvas. Segments can overlap each other, e.g., when edge-blended
projectors or passive stereo is used.

@@

A segment can define a frustum, in which case it overrides the default
frustum calculated from the canvas frustum and segment viewport.

{\footnotesize\lstinputlisting[firstline=225, lastline=246]
  {../../../equalizergraphics.com/documents/design/fileFormat.shtml}}

@@

Compound tasks describe the operations the compound executes. The
default is all tasks for compounds with no children (leaf compounds) and
\textsf{READBACK ASSEMBLE} for all others. The readback and assemble
tasks are only executed if the compound has output frames or input
frames, respectively. Tasks are not inherited by the children of a
compound.

@@

A swap barrier is used to synchronize the output of multiple
compounds. All swap barriers of the same name are synchronized The
default name is \textsf{barrier[.root\-Com\-pound\-Name]}. All windows
using the same \textsf{NV\_group} on a single system are synchronized
with each other using hardware synchronization. All groups using the
same \textsf{NV\_barrier} across systems are synchronized with each
other using hardware synchronization. When using hardware
synchronization, the barrier name is ignored.

@@

{\footnotesize\lstinputlisting[firstline=249, lastline=333]
  {../../../equalizergraphics.com/documents/design/fileFormat.shtml}}

>>>>

\date{
  \vspace{14cm}
\begin{textblock}{}(0,4.5)
  \hspace{-1cm}\includegraphics[width=22cm]{images/teaser.pdf}
\end{textblock} {\Large The official reference for developing and
  deploying parallel, scalable OpenGL\texttrademark\ applications using
  the Equalizer parallel rendering framework}\\\vspace{1cm}
Version 1.8.5 for Equalizer 1.2 \\[\medskipamount]
%  \today
}

@@

\clearpage
\pagenumbering{roman}
\pagestyle{headings}
\tableofcontents
%\clearpage
\listoffigures \vfill
\section*{Revision History}
{\center\begin{tabularx}{\textwidth}{|l|l|X|}
    \hline
    \bf Rev & \bf Date     & \bf Changes \\
    \hline
    1.0     & Oct 28, 2007 & Initial Version for Equalizer 0.4\\
    1.2     & Apr 15, 2008 & Revision for Equalizer 0.5\\
    1.4     & Nov 25, 2008 & Revision for Equalizer 0.6\\
    1.6     & Aug 07, 2009 & Revision for Equalizer 0.9\\
    1.8     & Mar 21, 2011 & Revision for Equalizer 1.0\\
    1.8.1   & Mar 25, 2011 & Minor Revision\\
    1.8.2   & Apr 04, 2011 & Added \sref{sFocusDistance}\\
    1.8.3   & Aug 10, 2011 & Rewrote \sref{sHello}\\
    1.8.4   & Nov 18, 2011 & Added \sref{sAutoConfig}\\
    1.8.5   & Jan 27, 2012 & RC review for Equalizer 1.2\\
    \hline
  \end{tabularx}}
\clearpage

@@

\begin{tabularx}{\textwidth}{|l|X|}
  \hline
  \textbf{Name} & EQ\_CONFIG\_FATTR\_EYE\_BASE\\
  \textbf{Value} & float\\
  \textbf{Default} & 0.05\\
  \textbf{Details} & The default distance in meters between the left and
  the right eye, i.e., the eye separation. The eye base influences the
  frustum during stereo rendering. See \sref{sTracking} for details.\\
  \textbf{See also} & EQ\_WINDOW\_IATTR\_HINT\_STEREO
  EQ\_COMPOUND\_IATTR\_STEREO\_MODE EQ\_CONFIG\_FATTR\_FOCUS\_DISTANCE
  EQ\_CONFIG\_IATTR\_FOCUS\_MODE\\
  \hline
\end{tabularx}\\\vfill

\begin{tabularx}{\textwidth}{|l|X|}
  \hline
  \textbf{Name} & EQ\_CONFIG\_FATTR\_FOCUS\_DISTANCE\\
  \textbf{Value} & float\\
  \textbf{Default} & 1.0\\
  \textbf{Details} & The default distance in meters to the focal plane. The
  focus distance and mode influence the calculation of stereo frusta. See
  \sref{sFocusDistance} for details.\\
  \textbf{See also} & EQ\_CONFIG\_IATTR\_FOCUS\_MODE
  EQ\_CONFIG\_FATTR\_EYE\_BASE\\
  \hline
\end{tabularx}\\\vfill

\begin{tabularx}{\textwidth}{|l|X|}
  \hline
  \textbf{Name} & EQ\_CONFIG\_IATTR\_FOCUS\_MODE\\
  \textbf{Value} & fixed \textbar relative\_to\_origin \textbar
  relative\_to\_observer\\
  \textbf{Default} & fixed\\
  \textbf{Details} & The mode how to use the focus distance. The
  focus maode and distance influence the calculation of stereo frusta. See
  \sref{sFocusDistance} for details.\\
  \textbf{See also} & EQ\_CONFIG\_IATTR\_FOCUS\_DISTANCE
  EQ\_CONFIG\_FATTR\_EYE\_BASE\\
  \hline
\end{tabularx}\\\vfill

@@

\begin{tabularx}{\textwidth}{|l|X|}
  \hline
  \textbf{Name} & EQ\_COMPOUND\_IATTR\_STEREO\_ANAGLYPH\_LEFT\_MASK\\
  \textbf{Value} & [ RED GREEN BLUE ]\\
  \textbf{Default} & [ RED ] \\
  \textbf{Details} & Select the color mask for the left eye pass during
  anaglyphic stereo rendering.\\
  \hline
\end{tabularx}\\\vfill

@@

{\footnotesize\lstinputlisting[firstline=89, lastline=98]
  {../../../equalizergraphics.com/documents/design/fileFormat.shtml}}

@@

{\footnotesize\lstinputlisting[firstline=100, lastline=109]
  {../../../equalizergraphics.com/documents/design/fileFormat.shtml}}

@@

A node represents a machine in the cluster, and is one process. It has a name, a
hostname, a number of connection descriptions and at least one pipe. The name of
the node can be used for debugging, it has no influence on the execution of
Equalizer. The host is used to automatically launch remote render clients. For a
description of node and connection attributes please refer to \sref{sGlobal}.

{\footnotesize\lstinputlisting[firstline=111, lastline=129]
  {../../../equalizergraphics.com/documents/design/fileFormat.shtml}}

@@

For the WGL window system, the device selects the \textit{n}th GPU in the
system. The GPU can be offline, in this case only PBuffer windows can be
used. To restrict the OpenGL output to the GPU, the
\textsf{WGL\_NV\_gpu\_affinity} extension is used when available. If the
extension is not present, the window is opened on the \textit{n}th monitor, but
OpenGL commands may be sent to a different or all GPU's, depending on the driver
implementation.

@@

{\footnotesize\lstinputlisting[firstline=130, lastline=139]
  {../../../equalizergraphics.com/documents/design/fileFormat.shtml}}

@@

{\footnotesize\lstinputlisting[firstline=141, lastline=162]
  {../../../equalizergraphics.com/documents/design/fileFormat.shtml}}

@@

Output channels are referenced in their respective segments. Source channels are
directly referenced by their respective source compounds.

@@

{\footnotesize\lstinputlisting[firstline=163, lastline=172]
  {../../../equalizergraphics.com/documents/design/fileFormat.shtml}}

@@

An observer represents a tracked entity, i.e, one user. It has a name, eye
separation and focal plane paramters. The name of an observer can be used for
debugging, it has no influence on the execution of Equalizer. It can be used to
reference the observer in views, in which case the name should be unique. Not
all views have to be tracked by an observer.

{\footnotesize\lstinputlisting[firstline=176, lastline=182]
  {../../../equalizergraphics.com/documents/design/fileFormat.shtml}}

@@

{\footnotesize\lstinputlisting[firstline=184, lastline=187]
  {../../../equalizergraphics.com/documents/design/fileFormat.shtml}}

@@

A view has a stereo mode, which defines if the corresponding destination channel
update the cyclop or left and right eye. The stereo mode can be changed at
runtime by the application.

@@

{\footnotesize\lstinputlisting[firstline=187, lastline=208]
  {../../../equalizergraphics.com/documents/design/fileFormat.shtml}}

@@

Each canvas consists of one or more segments. Segments can be planar or
non-planar to each other, and can overlap or have gaps between each
other. A canvas can define a frustum, which will create default planar
sub-frusta for its segments.

The layouts referenced by the canvas can be applied to it by the application at
runtime. One layout can be referenced by multiple canvases. The first layout is
the layout active by default, unless the command line option
\textsf{--eq-layout} was used to select another default layout.

A canvas may have a swap barrier, which becomes the default swap barrier for all
its subsequent segments. A swap barrier is used to synchronize the output of
multiple windows. For software swap synchronization, all windows using a swap
barriers of the same name are synchronized. Hardware swap synchronization is
used when a \textsf{NV\_group} is specified. All windows using the same
\textsf{NV\_group} on a single system are synchronized with each other using
hardware synchronization. All groups using the same \textsf{NV\_barrier} across
systems are synchronized with each other using hardware synchronization. When
using hardware synchronization, the barrier name is ignored.

{\footnotesize\lstinputlisting[firstline=211, lastline=236]
  {../../../equalizergraphics.com/documents/design/fileFormat.shtml}}

@@

A segment represents a single display, i.e., a projector or monitor. It
references a channel, has a name, viewport, frustum and potentially a swap
barrier. The name of a segment can be used for debugging, it has no influence on
the execution of Equalizer. It can be used to reference the segment, in which
case the name should be unique.

The channel referenced by the segment defines the output channel. The viewport
of the segment defines the 2D area covered by the channel on the
canvas. Segments can overlap each other, e.g., when edge-blended projectors or
passive stereo is used. The intersections of a segment with all views of all
layouts create destination channels for rendering. The destination channels are
copies of the segment's output channel with a viewport smaller or equal to the
output channel viewport.

@@

A segment can define a frustum, in which case it overrides the default
frustum calculated from the canvas frustum and segment viewport. A segment can
have a swap barrier, which is used as the swap barrier on the destination
compounds of all its destincation channels.

{\footnotesize\lstinputlisting[firstline=238, lastline=259]
  {../../../equalizergraphics.com/documents/design/fileFormat.shtml}}

@@

Compound tasks describe the operations the compound executes. The default is all
tasks for compounds with no children (leaf compounds) and \textsf{CLEAR READBACK
  ASSEMBLE} for all others. A leaf compound using the same channel as its parent
compound does not have a default clear task, since this has been executed by the
parent already. The readback and assemble tasks are only executed if the
compound has output frames or input frames, respectively. Tasks are not
inherited by the children of a compound.

@@

@@

{\footnotesize\lstinputlisting[firstline=262, lastline=333]
  {../../../equalizergraphics.com/documents/design/fileFormat.shtml}}
